Impact of Demographics and Skills of the Observer on Visual Statistical Inference

### 2012-09-07 sociology_paper.tex
abstract updated
table caption updated

\begin {abstract}  
Visual Inference is dependent on the careful evaluation of the lineups by individual observers. Each individual is different in their cognitive phycology and judiciousness which can affect the power of visual inference. To estimate the power of visual inference this can be controlled by getting evaluations from multiple people from a diverse population. But the other factor that may affect the power of visual inference is the demographics and skills of the observer. In this paper we examine this in details. The simulation experiments suggest that individual skill as well as demographics are very significant for the power of visual inference.

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6in]{learning_trend.pdf} 
   \caption{Probability of correct response for different attempts by each subjects for a plot with $p$-value=0.05 . The overall probability increases with attempts indicating a learning trend of the observers for experiments 1 and 3. For experiment 2 the overall trend trend is not statistically significant. Subject to subject variability is seen in learning pattern.}
   \label{fig:learning_trend}
\end{figure}

>>>>

\begin {abstract}  
Visual Inference is dependent on the careful evaluation of the lineups by individual observers. Each individual is different in their cognitive phycology and judiciousness which can affect the power of visual inference. To estimate the power of visual inference this can be controlled by getting evaluations from multiple people from a diverse population. But the other factor that may affect the power of visual inference is the demographics and skills of the observer. In this paper we examine this in details. The simulation experiments suggest that individual skill as well as demographics are very significant for the power of visual inference. Moreover, the data shows the evidence of learning or getting skilled while sequentially evaluating multiple lineups.

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6in]{learning_trend.pdf} 
   \caption{Probability of correct response for different attempts by each subjects for a plot with lineup difficulty ($p$-value of actual plot) = 0.05 . The overall probability increases with attempts indicating a learning trend of the observers for experiments 1 and 3. For experiment 2 the overall trend trend is not statistically significant. Subject to subject variability is seen in learning pattern.}
   \label{fig:learning_trend}
\end{figure}
